---
title: "Code I Learn"
author: "Shijie An"
date: "2022 Fall"
output: html_document
---

## Introduction to R
### 1. Vectors 
```{r example}
v <- c(140, -50, 20, -120, 240)
```
If we want to change names, we can do: 
```{r} 
poker_vector <- c(140, -50, 20, -120, 240)
names(poker_vector) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
## Define a new variable based on a selection
poker_wednesday <- poker_vector[3]
poker_days <- poker_vector[c(2:4)]
poker_days
```
If we want to select some results for Monday, Tuesday, and Wednesday
```{r}
poker_start <- poker_vector[c("Monday","Tuesday", "Wednesday")]
poker_start
```
We can have *logics* to see which day we make money
```{r}
selection_vector <- poker_vector > 0
selection_vector
```
And select from poker_vector these days
```{r} 
poker_winning_days <- poker_vector[selection_vector]
poker_winning_days
```

### class 1

the use of `seq()` and `rep()`

```{r}
s1 <- seq(1:10)
s2 <- seq(frome = 0, to = 100, by = 10)
r <- rep(c(1:3), times = 2, each = 3)
```

### class 2
open files
first you can set up your address by using `getwd()` and `setwd("")`
And then open files by typing `files <- read.csv("")`
```
states <- read.csv("/Users/anshijie/Desktop/D/CU TC/HUDK 5026 intro R/02 Vectors and Univariate/states.csv")
## or 
ath <- paste(c("/Users/anshijie/Desktop/", 
                "D/CU TC/HUDK 5026 intro R/",
                "02 Vectors and Univariate/states.csv"), 
              collapse = "")
path
statess <- read.csv(file = path)
```

### 2. Matrix







### 先放到一个地方

```{r echo = TRUE}
# generate a random seed
set.seed(1234)
# generate a sequence of 50 qnorms num
quant1 <- qnorm(p = seq(0.02, 1, 0.02))
plot(quant1, sort(income), 
     xlab = "Normal quantiles for 50 points", 
     ylab = "Incomes", 
     main = "Normal QQ plot")
abline(a = mean(income), b = sd(income), lwd = 2)
```
