---
title: "HW01"
author: "Shijie An"
date: "2022-09-09"
output: html_document
---

# Section 1
```{r first, comment="##"}
first <- c(1:10)
first
```
```{r second}
second <- seq(from = 0, to = 100, by = 10)
second
```
```{r third} 
third <- rep(x = seq(from = 1, to = 9, by = 2), each = 10)
third
```
In case I don't understand the numbered list correctly, I will put another list here. 
```{r numList} 
numList <- list(c(1:10), seq(from = 0, to = 100, by = 10),  rep(x = seq(from = 1, to = 9, by = 2), each = 10))
numList
```

# Section 2
```{r numeric}
x <- 10
x <- x + 1
x <- x * 5 + 1
x
```
# Section 3
```{r surprise}
## will print fibonacci number of first 10 digits
f <- numeric(10)
f[1] <- 1
f[2] <- 1
 for(i in 3:10) {
   f[i] <- f[i - 2] + f[i - 1]
 }
f
```

# plot
```{r plot, echo=FALSE}
x <- sample(1:10, size = 10, replace = TRUE)
y <- sample(1:10, size = 10, replace = TRUE)
plot(x = x, y = y, main = "My Graph", xlab = "x-axis", ylab = "y-axis", col = "red")
```

# features
## feature 1: code chuncks
The use of code chunks is very helpful, it provides us and convinient
 way to insert the code for other languages such as python, ds.js, or
 SQL. <br/>
 
## feature 2: Set Global Options
The "Set Global Options" really helps to make some options for our chunck code, such as the difference between ```comment = ""``` and ```comment = "##" ```gives the different prefix when we have our result printing out. <br/>

## feature 3: 
The RMarkdown can even insert tables here. When we have a sheet with our codes, we can output an good-looking visualized data from the output. That helps programmer to check with their data. For example: <br/>
```{r}
data <- faithful[1:4, ]
knitr::kable(data, caption = "Table with kable")
```