---
title: "HW02"
author: "Shijie An"
date: '2022-09-14'
output: html_document
---

## 1. 
```{r, echo=TRUE}
path <- "states.csv"
states <- read.csv(path)
```
```{r echo = TRUE}
income <- states[[3]]
income
length <- length(income)
length
class(income)
colnames(states[3])
```

## 2. 
```{r echo = TRUE} 
## the 5th element
states[5, ]
## the 50th element
states[50, ]
## 40th through 50th elements
states[40:50, ]
```

## 3. boxplots
Base R boxplot
```{r base R boxplot, echo = TRUE}
boxplot(income, 
        horizontal = TRUE, 
        xlab = "Incomes", 
        main = "US states Income in 1974 (base R plot)")
```

ggplot 2
```{r ggplot, echo = TRUE}
library(ggplot2)
ggplot(data = states, mapping = aes(x = income)) + 
  geom_boxplot() +
  xlab("Incomes") + 
  ggtitle("US states income in 1974 (ggplot2)")
```

```{r}
median(income)
quantile(income, probs = c(.25, .5, .75))
## so we have IQR = .75 - .25
# So Q1 = 3992.75, Q2 = 4519, Q3 = 4813.5
IQR <- 4813.50 - 3992.75
IQR
# So we have IQR = Q3 - Q1 = 820.75
# so the lower fence should be Q1 - 1.5 * IQR, which is: 
lower_fence <- 3992.75 - 1.5 * 820.75
lower_fence
# And upper fence should be Q3 + 1.5 * IQR, which is: 
upper_fence <- 4813.50 + 1.5 * 820.75
upper_fence
# So we can see that the lowest value, which is 3098, is within the lower fence of the income. 
# And the greatest number 6315 is beyond the upper fence, so it is an outlier. 
# So the second greatest income, 5348, is the greatest normal value showing in the boxplot. 
```

## 4. histograms
Base R histogram
```{r base R, echo = TRUE}
hist(income, breaks = seq(3000, 6500, 500), 
     xlab = "US states income in 1974 (base R histogram)", 
     main = "Frequency histogram with 7 bins")
```

ggplot2 histogram
```{r echo = TRUE}
ggplot(data = states, mapping = aes(x = income)) + 
  geom_histogram(breaks = seq(3000, 6500, 500), 
                 col = "red", fill = "cadetblue3") + 
  xlab("US states income in 1974 (ggplot2 histogram)") + 
  ggtitle("Frequency histogram with 7 bins")
```

Or we have have the histograms with 14 bins, so that will be like: 
```{r echo = TRUE}
ggplot(data = states, mapping = aes(x = income)) + 
  geom_histogram(breaks = seq(3000, 6500, 250), 
                 col = "red", fill = "cadetblue3") + 
  xlab("US states income in 1974 (ggplot2 histogram)") + 
  ggtitle("Frequency histogram with 14 bins")
```

For the 7 and 14 bins of histogram, I prefer the 14th, because it looks more clear. 
And with higher frequencies you will see different sections of income more clear. 

## 5. kernel density plots
Base R kernel density plot
```{r base R kernal density plot, echo = TRUE}
plot(density(income), 
     xlab = "US states income in 1974 (base R histogram)", 
     main = "Kernel Density plot")
```

ggplot2 kernel density plot
```{r, echo = TRUE} 
ggplot(data = states, mapping = aes(x = income)) + 
  geom_density(col = "steelblue", lwd = 1.05) + 
  xlab("US states income in 1974 (ggplot2 histogram)") + 
  ggtitle("Kernel Density plot")
```

The difference between kernel density plot and histogram is that the histogram 
looks more like being visualized by the discrete data, but kernel density plot
looks more like a continuous data. The kernel density plot is more likely to 
separate the bins in the histogram so that every "bin" of kernel density plot 
is some close number, so that the kernel looks to be more smooth. Histogram 
looks like a Riemann sum of the kernel density plot. 

## 6. QQ plots
Base R QQ plot
```{r echo = TRUE}
qqnorm(y = income, 
       ylim = c(3000, 6500), 
       main =  "Normal QQ plot for State Income in 1974 (base R)")
qqline(y = income)
```

ggplot qq plot
```{r echo = TRUE}
ggplot(data = states, mapping = aes(sample = income)) + 
  geom_qq(distribution = stats::qnorm) +
  geom_qq_line(distribution = stats::qnorm) +
  xlab("Theoretical normal quantiles") + 
  ylab("Samples quantiles") + 
  ggtitle("Normal QQ plot for state Income in 1974 (ggplot)")
```

The QQ plot indicates the hypothesis that the distribution of income is normally
distributed. The plots showed how scattered each point is aligned with the 
straight line. As each point is close to the straight line, that means the income
is more likely to be normal distributed. As we can see from this plot, each point
is close to the straight line, except the biggest num, which would be a outlier 
if we used in boxplot. We can also check if the income is normally distributed 
by using Shapiro-wilk normality test:
```{r echo = TRUE} 
shapiro.test(income)
```
We can see the value of W is close to 1, and the p-value is lower than 0.5, which
tells us that the sample data is almost normally distributed. 