---
title: "HW03"
author: "Shijie An"
date: "2022-09-22"
output: html_document
---

## 1. There is a a set in R called mtcars

### a. Is mtcars a data frame or a matrix? If it is not a data frame, make it one using data.frame(). 
```{r mtcars, echo = TRUE}
# typeof(mtcars)
class(mtcars)
# mtcars is a list, it is already a data frame. 
## mtcars <- data.frame(matrix(unlist(mtcars), nrow = length(mtcars), byrow = TRUE))
mtcars
```

### b. Access the help file on mtcars and summarize the brief description of the data set. 
```{r help file, echo = TRUE} 
?mtcars
## The mtcars is mainly talk about of 11 aspects of automobile design and 
## performance for 32 automobiles. It has several numeric variables such as mpg,
# of cylinders, displacement, gross horsepower, Rear axle ratio, weight, 1/4 
## mile time, engine, transmission, # of forward gears, # of carburetors. 
```

### c. Of the variables in mtcars all are of class numeric. That said, are there any that it would make sense to call categorical? Which ones and why?
```{r, echo = TRUE} 
str(mtcars)
## It can be seen that vs is categorical, because it is a nominal type of data 
## with only 0 = V-shaped, and 1 = straight options. am is also categorical, 
## because it is only 0 = automatic, and 1 = manual options . 
```

## 2.  Create a scatterplot of the relationship between horsepower (horizontal axis) and miles per gallon (vertical axis). Add a linear regression line to the  plot and describe the relationship in words in context. Do this in both base R and ggplot2.


## 3. Make a conditional violin plot with superimposed boxplots in ggplot2 of miles per gallon conditional on transition type (automatic or not). Interpret the plot in context.



## 4. Use factor() to add factor versions of the variables gear and cyl. Create dodged and stacked bar charts in ggplot2. For your stacked bar charts, look up how to normalize the bars so that they equal 100% and do that. Interpret the results in context.



### 5. Use mtcars data to create a scatterplot that pulls in multivariate information like we did with the state abbreviations and regions in class. Surprise me.