---
title: "HW04"
author: "Shijie An"
date: '2022-09-27'
output: html_document
---
```{r preload}
library(ggplot2)
load("/Users/anshijie/Desktop/D/CU TC/HUDK 5026 intro R/HUDM5026_R_HW/acupuncture.Rdata")
```
## 1. Find the minimum (see function min(), 1st quartile (i.e., 25th percentile; see function quantile(), median (see function median(), 3rd quartile (i.e., 75th percentile; see function quantile()), and maximum (see function max() values of pk1 and pk5
```{r question1, include=FALSE}

## minimum
min(acupuncture$pk1, na.rm = TRUE)
min(acupuncture$pk5, na.rm = TRUE)
## 1st quantile 
quantile(acupuncture$pk1, probs = 0.25)
quantile(acupuncture$pk5, probs = 0.25)
## median
median(acupuncture$pk1, na.rm = TRUE)
median(acupuncture$pk5, na.rm = TRUE)
## 3st quantile 
quantile(acupuncture$pk1, probs = 0.75)
quantile(acupuncture$pk5, probs = 0.75)
## maximum
max(acupuncture$pk1, na.rm = TRUE)
max(acupuncture$pk5, na.rm = TRUE)
```

## 2. Write a function that calculates the min, Q1, median, Q3, and max values of a vector. Then, apply the function to age, sex, migraine, chronicity, pk1 and pk5
```{r question2}
## @param acu acupuncture
## @return out min, q1st, median, q3st, max
call_out <- function(acu) {
  min <- min(acu, na.rm = TRUE)
  q1st <- quantile(acu, probs = .25)
  median <- quantile(acu, probs = .5)
  q3st <- quantile(acu, probs = .75)
  max <- max(acu, na.rm = TRUE)
  out <- c(min, q1st, median, q3st, max)
  out
}
call_out(acupuncture$age)
call_out(acupuncture$sex)
call_out(acupuncture$chronicity)
call_out(acupuncture$pk1)
call_out(acupuncture$pk5)
# by(data = acupuncture$age,
#    INDICES = acupuncture$group,
#    FUN = call_out, 
#    na.rm = TRUE)
```

## 3. Summarize the output from the last item in a table. Use R Markdown to make a table - see here

|            | min  | q1st  | median | q2st  | Max   |
| ---------- | ---- | ----- | ------ | ----- | ----- |
| age        | 18   | 41    | 48     | 54    | 65    |
| sex        | 0    | 1     | 1      | 1     | 1     |
| chronicity | 1    | 10    | 20     | 31    | 54    |
| pk1        | 6.75 | 14.50 | 20.25  | 33.00 | 94.75 |
| Pk5        | 0.00 | 8.50  | 15.00  | 25.25 | 87.25 |



## 4. Write a function that plots a boxplot of a vector and also reports the min, Q1, median, Q3, and max. Then apply the function to pk1 and pk5. Tip: use your function from the last part to help you write this function.
```{r plot} 
box_plot <- function(acu) {
  min <- min(acu, na.rm = TRUE)
  q1st <- quantile(acu, probs = .25)
  median <- quantile(acu, probs = .5)
  q3st <- quantile(acu, probs = .75)
  max <- max(acu, na.rm = TRUE)
  boxplot(acu, horizontal = TRUE)
}
box_plot(acupuncture$pk1)


```

