---
title: "HW05"
author: "Shijie An"
date: '2022-10-04'
output: html_document
---

```{r setup}
library(tidyverse)
```

1. Import the data using `read_csv()` and call it `acu`. Note that the data have a header row.
```{r}
acu <- read.csv("acupuncture.csv")
```

2. Use base R to calculate the mean and sd for each variable in the data set using `apply()`
```{r}
## mean for each element
apply(acu, MARGIN = 2, mean)
## sd for each element
apply(acu, MARGIN = 2, sd)
```

3. Use the `by()` function to calculate the mean `pk5` score by treatment group. Are you
comfortable making a conclusion about the efficacy of acupuncture based on these
means? Why or why not?
```{r}
by(
  data = acu$pk5, 
  INDICES = acu$group, 
  FUN = mean
)
## It cannot be concluded about efficacy by only telling the relationship of group and severity of pk5. It needs more information other than groups. 
```

4. Use base R to create a new variable called `diff` by calculating the difference score
(post - pre) for headache severity rating.
```{r}
diff <- acu$pk5 - acu$pk1
acu <- mutate(acu, diff)
acu$diff
```

5. Use base R to create a new variable called `remission` that is a 1 if a person’s score
dropped by 10 points or more and a 0 if not.
```{r}
acu <- mutate(acu, remission <- ifelse(diff <= -10, 1, 0))
acu$remission
```

6. Use tidyverse functions to replicate (3) - (5), calling the variables `diff2` and `remission2`
```{r}
acu %>% 
  group_by(group) %>% 
  summarize(mean(pk5))
acu <- acu %>% 
  mutate(diff2 = pk5 - pk1)
acu$diff2
acu <- acu %>% 
  mutate(remission2 = ifelse(diff2 <= -10, 1, 0))
acu$remission2
```

7. Create a scatterplot of baseline headache severity rating (horizontal axis) vs 1-year
headache severity rating (vertical axis) using base R.
```{r}
plot(acu$pk1, acu$pk5, xlab = "PK1", ylab = "PK5",
     main = "baseline headache severity rating vs 1-year headache severity rating")
```

8. Use `ggplot2`to replicate (7).
```{r}
acu %>%
  ggplot(aes(x = pk1, y = pk5)) + 
  geom_point() + 
  xlab("PK1") + 
  ylab("PK5") + 
  ggtitle("aseline headache severity rating vs 1-year headache severity rating")
```

9. In either base R or ggplot2, take your pick, incorporate information on treatment
group and sex into the plot. Consider using color, point character, point size, or other
graphical elements. Be sure to include a legend.
```{r}
acu %>% 
  mutate(group = factor(x = group,
                           labels = c("Group 0", "Group 1"),
                           levels = c(0, 1)),
            sex = factor(x = sex,
                         labels = c("male", "female"),
                         levels = c(0, 1))) %>%
  ggplot(aes(x = pk1, y = pk5, color = group, shape = sex))  + 
  geom_point() + 
  scale_color_manual(values = c("#89ABE3FF", "#EA738DFF")) + 
  ggtitle("aseline headache severity rating vs 1-year headache severity rating")
```

10. Try to replicate what you did in (9) with the other plotting platform. I.e., if you used
base R, now try to replicate using ggplot (or vice versa)
```{r}
plot(acu$pk1~ acu$pk5, xlab = "PK1", ylab = "PK5", 
     col = factor(acu$sex), 
     pch = acu$group,
     main = "baseline headache severity rating vs 1-year headache severity rating")
legend(
  x = "bottomright",
  legend = c("Group 0", "Group 1", "male", "female"),
  title = "Group and Sex",
  col = c("red", "black", "black", "black"), 
  pch = c(16, 16, 1, 0)
)
```
