---
title: "HW07"
author: "Shijie An"
date: '2022-10-12'
output: html_document
---

```{r setup}
## have to install packages for "AMCP"
library(AMCP)
library(tidyverse)
```

1. Rename the data set `dat1`.
```{r}
data("C11E19")
dat1 <- C11E19
```

2. Each row of `dat1` represents data from a different participant. Add a participant `ID`
number column to the data set and call it `ID`.
```{r}
dat1 <- dat1 %>% 
  mutate(ID = row_number(), .before = Face)
dat1
```

3. Create `dat1_long` by pivoting `dat1` from wide to long. When you pivot, name the
new column that will hold the categorical values (Face, Circle, Newspaper, and White)
`target` and name the new column that will hold the numeric outcome data `gaze_time`.
```{r}
dat1_long <- dat1 %>% 
  pivot_longer(cols = Face : White, 
               names_to = "target", 
               values_to = "gaze_time")
dat1_long
```

4. Use `summarize()` and `group_by()` with `dat1_long` to find the sample mean for each
child for each target (Face, Circle, Newspaper, and White)
```{r}
dat1_long %>% 
  group_by(target) %>% 
  summarize(mean(gaze_time))
```

5. Use `ggplot()` with `dat_long` to create a conditional boxplot that has separate boxplots
of gaze time for each target (Face, Circle, Newspaper, and White)
```{r}
dat1_long %>% 
  ggplot(aes(x = target, y = gaze_time)) + 
  geom_boxplot()
```