---
title: "HW08"
author: "Shijie An"
date: '2022-10-26'
output: html_document
---

Check this URL: https://sicss.io/2018/materials/day3-text-analysis/basic-text-analysis/rmarkdown/Basic_Text_Analysis_in_R.html
```{r setup}
library(tidyverse)
aiw <- read_file(file =  "https://www.gutenberg.org/files/11/11-0.txt")
```

1. How many characters does *aiw* contain? Is it a vector? What is the length of the vector?
```{r}
nchar(aiw)
is.vector(nchar(aiw))
length(nchar(aiw))
sprintf("There are %d characters in aiw. ", nchar(aiw))
print("nchar(aiw) is a vector")
sprintf("The vector has a length of %d", length(nchar(aiw)))
```


2. Examine the first 3000 characters of the text of the book with `str_sub()`.
```{r}
str_sub(aiw, end = 3000)
# nchar(str_sub(aiw, start = 1, end = 3000))
```

3. Note that when imported, the text file brought along some formatting in the way of
`"\n"` and `"\r"` strings. Find and replace these white space using `str_replace_all()` and
save the output as *aiw2*.
```{r}
# aiw2 <- str_replace_all(aiw, c("\r", "\n"), "-") 不知道为啥不行
## better way: 
## aiw2 <- gsub("\r|\n", "",aiw)
aiw2 <- str_replace_all(aiw, c("\r" = "", "\n" = ""))
aiw2
```

4. Project Gutenberg has added some text at the beginning and appended some legal
boilerplate text to the end. Find the true beginning and ending of the text and save only the
book text (i.e., drop off the boilerplate). Save this as *aiw2*.
```{r}
## start by :[Illustration]
## end by : THE END
# str_detect(aiw, "[Illustration]")
# str_detect(aiw, "THE END")
start <- str_locate(aiw, "Illustration]")
end <- str_locate(aiw, "THE END")
aiw2 <- str_sub(aiw, start[2] + 1, end[2])
aiw2
```

5. Note that *aiw2* is a single long character string. We would like to separate the words
so that each is it’s own element of a character vector. So, once Task 2 is accomplished, use
str_split() to do that and rename the result to *aiw3*. This will produce output in a list,
but we want a vector, so use `unlist()` on *aiw3* to turn it into a long character vector; again,
save the output as *aiw3* here.
```{r}
aiw3 <- unlist(str_split(aiw2, " "))
```

6. What proportion of words in the book contain at least one uppercase letter?
```{r}

```

7. What proportion of words in the book use some form of punctuation?
```{r}

```

8. Alice in Wonderland is one of the most influential books for children written over the
past 200 years. As an example, ever wonder why Nintendo’s Super Mario grows when he eats
a mushroom? Although Shigeru Miyamoto (Mario’s creator) has more recently denied a direct
influence, he has spoken in the past about how he was thinking about Alice in Wonderland
while creating the video game. How many times does the word "mushroom" occur in the
text, regardless of letter case? Locate each instance of the word and print out enough of the
surrounding text to display the context for each instance.
```{r}

```

9. Use a function we have discussed to replace all instances of the word ‘mushroom’
with the word *‘apple’*.
```{r}

```